Enhanced proximity effect in zigzag-shaped Majorana Josephson junctions.

### 2019-03-12 paper/snakemajoranas.tex
format bibfile

\comment{The gap is small because of long trajectories.}
An important challenge in creating stable Majoranas is the appearance of a soft gap---a power law, instead of exponential decay of the density of states near zero energy.
It was shown previously that interface disorder and pairbreaking lead to a soft induced gap~\cite{takei_soft_2013}.
Even in systems with perfect interfaces and the absence of pairbreaking, states which have their momentum directed along the junction give rise to a soft gap~\cite{de_gennes_1963, beenakker_billiards_2005}.
From a semiclassical perspective, these momenta correspond to long paths through the semiconductor without interruption by the superconductor, shown in Fig.~\ref{fig:setup}(a).
These long trajectories have long flight times $\tau_\textrm{f} \approx L_\textrm{t} / v_F$ (see Fig.~\ref{fig:setup}), where $L_\textrm{t}$ is the trajectory length.
Equivalently, the Thouless energy of these trajectories $E_{\textrm{Th}}=\hbar / \tau_\textrm{f}$ is small, resulting in a small gap $E_\textrm{gap} \ll \Delta$.
This problem does not appear when the Fermi surface is small and the zero point motion dominates the transverse velocity, making a low filling of the bands a possible workaround\cite{Nijholt2015}.
However, low filling requires precise knowledge of the system and is more sensitive to disorder or microscopic inhomogeneities.
On the other hand, disorder scatters these long trajectories and introduces a cutoff on the scale of the mean free path~\cite{Haim2018}; however, disorder is impossible to control to a required precision experimentally.

>>>>

\comment{The gap is small because of long trajectories.}
An important challenge in creating stable Majoranas is the appearance of a soft gap---a power law decay instead of an exponential decay of the density of states near zero energy.
It has been shown that interface disorder, pairbreaking, tunnel barrier to normal leads, temperature, and having multiple modes with different transmission probabilities, and dissipation can cause a soft induced gap~\cite{Takei2013,Liu2017,Stanescu2014}.
However, even without the aforementioned causes, a soft gap would still appear due to states with their momentum parallel to the junction~\cite{Gennes1963,Beenakker2005}.
From a semiclassical perspective, these momenta correspond to long paths through the semiconductor without interruption by the superconductor, shown in Fig.~\ref{fig:setup}(a).
These long trajectories have long flight times $\tau_\textrm{f} \approx L_\textrm{t} / v_F$ (see Fig.~\ref{fig:setup}), where $L_\textrm{t}$ is the trajectory length.
Equivalently, the Thouless energy of these trajectories $E_{\textrm{Th}}=\hbar / \tau_\textrm{f}$ is small, resulting in a small gap $E_\textrm{gap} \ll \Delta$.
This problem does not appear when the Fermi surface is small and the zero point motion dominates the transverse velocity, making a low filling of the bands a possible workaround\cite{Nijholt2015}.
However, low filling requires precise knowledge of the system and is more sensitive to disorder or microscopic inhomogeneities.
On the other hand, disorder scatters these long trajectories and introduces a cutoff on the scale of the mean free path~\cite{Haim2018}; however, disorder is impossible to control to a required precision experimentally.
